Parallel global optimization algorithm employing decision trees for launching local methods

### 2025-09-17 2025/MMST_DecisionTree/ParallelDecisionTree.tex
minor corrections in formulas

	\item Extract $c = \max(p, |U|)$ trial point coordinates $y^{k+1}=y\left(x^{k+1}\right) ... y^{k+c}=y\left(x^{k+c}\right)$ from the set $U$ (which contains trial point coordinates). If $c < p$, then first perform trials at $n = p - c$ points according to Steps~2--7; otherwise proceed directly to Step~8.

@@

	\item Compute the coordinates of the new trial points $y'^{k+j}=y\left(x^{k+j}\right), \ 1\leq j\leq n$, whose preimages are  $x^{k+j}\in\left(x_{t_j-1},x_{t_j}\right)$, according to the following formula:
	\begin{equation}
		\label{agp5_x1}
		x^{k+1}=\frac{x_t+x_{t-1}}{2}-\mathrm{sign}\left(z_t-z_{t-1}\right)\frac{1}{2r}\left[\frac{\left|z_t-z_{t-1}\right|}{M}\right]^N.
	\end{equation}

@@

	\item Receive trial values from all $p$ processes and add them to the search information.

@@

	\item For all points $y' \in V$, find the points $y'_q$ closest to $y'$.

	If no point $y'_q$ has a value smaller than $y'$, add $y'$ to the set $U$.

	Clear the set $V$.

>>>>

	\item Extract $c = \max(p, |U|)$ trial point coordinates $y^{k+1}=y\left(x^{k+1}\right),...,y^{k+c}=y\left(x^{k+c}\right)$ from the set $U$ (which contains trial point coordinates). If $c < p$, then first perform trials at $n = p - c$ points according to Steps~2--7; otherwise proceed directly to Step~8.

@@

	\item Compute the coordinates of the new trial points $y'^{k+j}=y\left(x^{k+j}\right), \ 1\leq j\leq n$, whose preimages are  $x^{k+j}\in\left(x_{t_j-1},x_{t_j}\right)$, according to the following formula:
	\begin{equation}
		\label{agp5_x1}
		x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}-\mathrm{sign}\left(z_{t_j}-z_{t_j-1}\right)\frac{1}{2r}\left[\frac{\left|z_{t_j}-z_{t_j-1}\right|}{M}\right]^N.
	\end{equation}

@@

	\item Receive trial results from all $p$ processes and add them to the search information.

@@

	\item For all points $y' \in V$, find the points $y'_q$ closest to $y'$.
		If no point $y'_q$ has a value smaller than $y'$, add $y'$ to the set $U$.
		Clear the set $V$.
